How Important are Usage Examples in REST API Documentation?

### 2017-03-08 controlled_study.tex
add graph about time

\begin{subfigure}{0.5\textwidth}
\centering

\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Trial API Calls,
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

@@

    \addplot[smooth,mark=*,black] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {grouptwo_success.csv};
      \addlegendentry{G2: Using Forked}
    \end{axis}

\end{tikzpicture}
\caption{Trial vs. Successful API Calls}
\label{graph:productivity}

\end{subfigure}

\begin{subfigure}{0.5\textwidth}
\centering

\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Time Spent (minutes),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=Time] {groupone_time.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=Time] {grouptwo_time.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

\end{tikzpicture}
\caption{Average Time Spent}
\label{graph:time}

\end{subfigure}

\begin{subfigure}{0.5\textwidth}
\centering

\end{subfigure}

@@

In Figure \ref{graph:productivity} we see that, for the simpler tasks T2 and T3, G1 had used more trial API calls on average and reached successful answers with a lower percentage compared to G2. For T4, where the participants are required to inspect a HTTP response header, G2 needed more API calls on average, but also yielded 24\% higher success rate. For the more complicated tasks T5 and T6, we see that participants in G1 had very low success rate and very high number of average API trials compared to G2. The data here clearly depicts that without usage examples REST API client developers require more trial and error attempts yet resulting in lower success rates, and the situation gets worse for relatively complicated tasks.

>>>>

\begin{subfigure}{0.5\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Trial API Calls,
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {groupone.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=AverageAPICalls] {grouptwo.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

@@

    \addplot[smooth,mark=*,black] table [col sep=comma, x expr=\coordindex, y=SuccessRate] {grouptwo_success.csv};
      \addlegendentry{G2: Using Forked}
    \end{axis}
\end{tikzpicture}
\caption{Trial vs. Successful API Calls}
\label{graph:productivity}
\end{subfigure}
\begin{subfigure}{0.4\textwidth}
\centering
\begin{tikzpicture}
    \begin{axis}[
        ybar,
        xtick=data,
        xticklabels from table={\groupone}{Task},
        legend style={at={(0.5,-0.15)},
        anchor=north,legend columns=-1},
        ylabel=Average Time Spent (minutes),
        width=2.8in
    ]
    \addplot[pattern=crosshatch dots, pattern color=gray] table [col sep=comma, x expr=\coordindex, y=Time] {groupone_time.csv};
    \addplot[draw=black] table [col sep=comma, x expr=\coordindex, y=Time] {grouptwo_time.csv};
    \legend{G1: Using Original, G2: Using Forked}
    \end{axis}

\end{tikzpicture}
\caption{Average Time Spent}
\label{graph:time}
\end{subfigure}

@@

In Figure \ref{graph:productivity} and  \ref{graph:time} we see that, for the simpler tasks T2 and T3, G1 had used more trial API calls and more time on average and reached successful answers with a lower percentage compared to G2. For T4, where the participants are required to inspect a HTTP response header, G2 needed more API calls on average, but also yielded 24\% higher success rate. For the more complicated tasks T5 and T6, we see that participants in G1 had very low success rate and very high number of average API trials compared to G2. The data here clearly depicts that without usage examples REST API client developers spend more time and require more trial and error attempts yet resulting in lower success rates, and the situation gets worse for relatively complicated tasks.

\begin{figure}[h]
\centering

\end{figure}
